Cluster Analysis

### 2020-07-31 MSDS 411 assign 4.Rmd
changing output

---
title: 'Cluster Analysis'
author: "Nadia Noui-Mehidi"
date: "11/5/2019"
output:
  word_document: default
  pdf_document: default
---

@@

In this project I perform an exploratory data analysis for three different clustering problems.

>>>>

---
title: 'Cluster Analysis'
author: "Nadia Noui-Mehidi"
date: "11/5/2019"
output: rmarkdown::github_document

---

@@

In this project I perform an exploratory data analysis on clustering problems. The project is divided into three sections, each focusing on a different dataset and cluster analysis technique. This project includes applications of hierarchical cluster analysis, k-means cluster analysis, the integration of principal components analysis and cluster analysis, and the application of cluster analysis as a predictive model.
